Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-10-23 thesis/paper_draft.qmd
minor change

{\huge \bfseries Enhancing Forecast Reconciliation:\\
A Study of\\
Alternative Covariance Estimators\par}

@@

```{r tourism-probscores}
#| label: fig-tourism-probscores
#| fig.height: 10
#| fig.width: 10
#| fig-cap: "Percentage relative improvement in the Winkler score at 80% and 95% nominal coverage, CRPS, and Energy score of multiple reconciled forecasts over the base forecasts for the Australian domestic tourism data, for 1-step-ahead forecasts. The positive (negative) entries indicate a decrease (increase) in the probabilistic scores relative to base."

>>>>

{\huge \bfseries Enhancing Forecast Reconciliation:\\
A Study of Alternative Covariance Estimators\par}

@@

```{r}
#| label: fig-tourism-probscores
#| fig.height: 10
#| fig.width: 10
#| fig-cap: "Percentage relative improvement in the Winkler score at 80% and 95% nominal coverage, CRPS, and Energy score of multiple reconciled forecasts over the base forecasts for the Australian domestic tourism data, for 1-step-ahead forecasts. The positive (negative) entries indicate a decrease (increase) in the probabilistic scores relative to base."
